%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{cv/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-skyblue}
%\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{Hannah M.}{Gallagher}
\address{Willing to relocate. Rochester, NY, 14610} 
\mobile{(585)-313-8838} 
%%% Social
%\email{hg4285@rit.edu}		Find a way to put both emails here!
\email{ hgallagher477@gmail.com}
%\homepage{URL goes here}
\github{hgallagh}
\linkedin{Hannah Gallagher}
%%% Optionals
\position{Data Scientist{\enskip\cdotp\enskip} Physicist}
\quote{
\textbf{Present Academia Research:} \\ 
My research interests focus on analytic approximations to the Einstein field equations of highly spinning, precessing black hole binaries, including post-Newtonian approximations, black hole perturbation theory, and post-Minkowski expansions. These sources are more astrophysically motivated than their non-spinning counterparts. Understanding these black hole binaries will be crucial for the next stages of multi-messenger astronomy.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Hannah M. Gallagher~~~·~~~Curriculum Vitae}
  {\thepage}

\begin{document}
%%% Make a header for CV with personal data
\makecvheader

\vspace{1.0mm}
\begin{justify}
\bodyfont\itshape\color{darktext}
\textbf{Broader Technical Introduction and Career Goals:} \\ 
I am primarily enthusiastic about laser research and development driven roles. I have been collaborating within LIGO for over two years now in CBC so a company with version control standards is a must. I thrive in high stress environments as those are where the real work occurs. I am looking for project management and experiment design roles to aid incoming scientists while still learning from lead researchers. I am always searching for new ways to expand my skill set and wish to increase my scientific h-index and collaborate via conferences through APS ,OSA, and SPIE. Any guidance and points to professional textbooks and papers are welcome. I would love the ability to be sponsored for higher security clearance.   
\end{justify}
\vspace{1.0mm}

%%% Import contents
\import{\sectiondir}{experience.tex}
\import{\sectiondir}{presentation.tex}
%\import{\sectiondir}{writing.tex}
\import{\sectiondir}{education.tex} 
\import{\sectiondir}{extracurricular.tex}
\import{\sectiondir}{skills.tex} 

%\import{\sectiondir}{teaching.tex}
%\import{\sectiondir}{committees.tex}
\vspace{3.0mm}
\import{\sectiondir}{outreach.tex}
\vspace{3.0mm}
\import{\sectiondir}{honors.tex}
%\vspace{3.0mm}
%\import{\sectiondir}{awards.tex}

\end{document}
