\cvsection{Education}
\begin{cventries}
 \cventry
    {University of Rochester}
    {Optical Engineering}
    {Rochester, NY}
    {Aug. 2014 - May 2017}
    {
      \begin{cvitems}
        \item {Double Major in English}
        \item {Transferred to RIT for scholarship received. Taught me to be in charge of my education and skill development.}
      \end{cvitems}
      
   }
   
\cventry
    {University of Rochester}
    {Optical Engineering}
    {Rochester, NY}
    {Aug. 2014 - May 2017}
    {
      \begin{cvitems}
       \item{Double Major in English}
       \item{Transferred to RIT for scholarship received.  Taught me to be in charge of my education and skill development.}
       \item{Made and kept life long friends and colleagues in the program. Majority of the time we rock climb, play pick up sports, bike, and run together.}
      \end{cvitems}
   }

   
 \cventry
    {Rochester Institute of Technology}
    {Applied and Computational Mathematics BS to Astrophysics Graduate Student}
    {Rochester, NY}
    {Aug. 2018 - Present}
    {
      \begin{cvitems}
       \item{I am currently doing Numerical Relativity and Bayesian Statistics Research for LIGO as a collaborator and working towards my Astrophysics PhD at the 700 level}
      \end{cvitems}
   }


     \cventry
    {Relevant classes taken during undergraduate to graduate relating to the field}
    {Relevant Coursework and Study}
    {Rochester Institute of Technology; University of Rochester}
    {}
    {
      \begin{cvitems}
        \item{Nonlinear-Gaussian Beams, two-beam coupling, raman scattering}
        \item{Polarization-electromagnetic theories, polarization in multilayers and gratings, principles of polarization effects in focusing and imaging, polarization metrology, and topics in polarization coherence.}
        \item{General Relativity-Tensor Algebra}
        \item {Topology Independent Study - Topology fundamentals with an emphasis on black holes and general relativity}
        \item{Sensors and Detectors- Optical Science and calculations behind the technology}
        \item {Mathematical Methods in Optics - Boundary Value Problems course pertaining to optics}
        \item {Interference and Diffraction- Optical Engineering course on the propagation of light}
        \item {Mathematical Modeling- Research paper literacy and formulation and presentation of unique natural mathematical research}
        \item {Geometrical Optics - Studied the different properties of various lens systems with Code V}
        \item {Real Analysis - Applied Math course with heavy emphasis on proofs}
        \item {Numerical Linear Algebra- Theoretical math with applications in computer science and proficiency in Matlab packages in matrix processing}
        \item {Linear Algebra with Differential Equations- Compact course to solve differential equations with advanced linear algebra}
      \end{cvitems}
    }

   

%   \cventry
%      {RIT}
%      {Dissertation Title}
%      {Rochester NY}
%      {SCARY DEFENSE DATE}
%      {
%			\begin{cvitems}
%			\item{Zippy one-liner: Many technical words all in a row}
%			\end{cvitems}
%		}
\end{cventries}
