\cvsection{Professional Appointments}
\begin{cventries}

    \cventry
    {Undergraduate to Graduate Research Assistant}
    {Rochester Institute of Technology}
    {Rochester, NY}
    {Jan. 2020 - Present}
    {
      \begin{cvitems}
        \item {Run, test, analyze algorithm development (RIFT Parameter Estimation and waveforms) pertaining to LIGO gravitational wave data (real and fiducial waveforms) in varying levels of complexity as my case and problem is a stress test case for efficiency. Transitioned from low-level and assembly language makefiles to applications.}
        \item{Teach and oversee incoming undergraduate and graduate student collaborators on RIFT complexities and relevant science. Provide wikipedia pages for a more streamline intake.}
        \item{Present research at webinars and at the lab, meet with visiting postdocs and scholars.}
        \item{Baysian statistics to numerical relativity with necessary knowledge of astrophysics (whitepapers and gitlabs firehouse on computational efficiency, packages, and relevant precessing binaries and black hole neutron star papers)}
        \item{Transferring was a life lesson in "university specific courses" and most of my education has turned into independent studies and my research advisors giving me more advanced topics while in a course}
        \item{Implement(ed) various numerical methods and recipes for  computational efficiency}
        \item {Report(ed) insights and generate(d) statistical plots to the project's research group}
        \item {Collaborator on paper and in the research group (What I did in the pandemic so worked on it all the time and remote via clusters and mattermost/teamspeak)}
        \item {Languages, Software, and Equipement used: Python, and LaTex, GitLabs, CondorQ, Hanford and Caltech Cluster, RIFT, TensorFlow}
        \item{O3 Development was a life lesson for large collaboration version control and CBC communication}
        \item{Passion project: Used Fedora distribution (Linux) solely on old Laptop since 2019 for merger research and personal laptop to learn the fundamentals}
      \end{cvitems}
    }
    \cventry
    {Calculus 182A TA}
    {Rochester Institute of Technology}
    {Rochester, NY}
    {Aug. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Aided calculus students with key concepts in workshop and office hours: integration techniques and identities}
        \item {Graded quizzes and homework}
      \end{cvitems}
    }
  \cventry
    {Junior Data Scientist}
    {Soleo Communications}
    {Victor, NY}
    {Sept. 2017 - Aug. 2019}
    {
      \begin{cvitems}
        \item {Wrote natural language scripts to further analyze and optimize the company's telecommunication systems}
        \item {Daily Scrum stand up meetings and sprints in an Agile environment for the software engineering team}
        \item {Provided solutions in business intelligence meetings to bridge the gap between account management and software development as junior tester and debugger}
        \item{Communicated what was possible to be programmed for legal team, account managers, and }
        \item{Google Ad words}
        \item{Languages used:Python, HiveQL, Java, Pentaho}
      \end{cvitems}
    }

  \cventry
    {IRAD Optical Fiber Intern}
    {Vencore Optical Engineering Intern}
    {Reston, VA}
    {May 2017 - Aug. 2017}
    {
      \begin{cvitems}
        \item {Simulated the optical systems and models to provide a software efficiency evaluation between Matlab and Python}
        \item{Analyzed cybersecurity vulnerabilities }
        \item{Waveguide and undersea fiber networks IRAD Scif work. \\Learned the fundamentals of fiber optics and optical communication
    systems via lecture, guided discussion, and reference materials. Topics
    included waveguide fabrication, properties of light (amplitude,
    frequency, phase, polarization), power, attenuation, optical
    signal-to-noise ratio, modulation (OOK, BPSK, DP-QPSK), dispersion,
    bandwidth, wavelength-division multiplexing, baud rate, and optical
    amplification (EDFA). \\ Learned about working in the field of cleared government contracting
    via a series of brown bag discussions with experienced professionals.
    Topics include security considerations (SF-86, Financial Disclosure
    Form, background investigation, polygraph), the proposal process
    (shaping, market survey, draft RFP, final RFP, proposal volumes),
    working for the government (COTR presentation), program
    management (FTE, CPAF/CPFF, ECPs, contract extensions), data
    analytics [TBD], and presentation skills (elevator pitches,
    chartsmanship). }
    \item{Sponsored for Polygraph test and turned down full-time offer to make sure higher education comes first. }
      \end{cvitems}
    }

  \cventry
    {Research Assistant}
    {Laser Lab for Energetics Research Assistant}
    {University of Rochester}
    {Jan. - May 2017}
    {
      \begin{cvitems}
        \item {Clean room monitored a polarizer laser system and implemented scientific tools for lead scientists to analyze the incoming dataset}
        \item {Languages used: Matlab, SQL}
        \item {General project documentation and technical writing for research advisor}
      \end{cvitems}
    }
        
  \cventry
    {Quality Assurance Measurement Technician Intern}
    {Optimax Technician Intern}
    {Webster, NY}
    {Jan. 2016 - May. 2016}
    {
      \begin{cvitems}
        \item {Made rounds and inspected lens and procedures by other manufacturing technicians}
        \item{Learned the qualities and procedures of how each lens was fabricated and coated}
        \item{Provided analysis and orders on the relevant lenses}
        \item{Learned procedures of a optical manufacturing plant}
      \end{cvitems}
    }    

    
  \cventry
    {Data Analyst}
    {Soleo Communications Data Analyst}
    {Victor, NY}
    {Mar. 2013 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Provided updates on revenue fluctuation and feedback on the company's API taxonomy mapping errors}
        \item{Worked with excel macros and aided financial controller in the monthly close}
        \item{Picked up Front Desk Responsibility of interview intake and recruitment during the interim hiring process ( Start-Up Roles)}
      \end{cvitems}
    }    
%  \cventry
%    {Intern}
%    {Respec Inc.}
%    {Rapid City, SD}
%    {Summer 2012}
%    {
%      \begin{cvitems}
%        \item {Created a 3-D finite volume analysis grid for stability analysis of salt mines.}
%       \end{cvitems} 
%    }
%  \cventry
%    {Science Intern}
%    {Sanford Underground Lab}
%    {Lead, SD}
%    {Summer 2011}
%    {    
%      \begin{cvitems}
%        \item {Assisted in the setup of the Majorana experiment, electrolyzed copper for machining instrumentation, and implemented  lead shielding.}
%      \end{cvitems}
%    }
\end{cventries}
